Untitled

### 2024-11-21 code/manuscript_altanalysis.Rmd
i promise, final figures

  outlier.vals <- quantile(df.temptemp$Altman, p = c(0.01, 0.99), na.rm = TRUE)
   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)) %>% mutate(Altman = ifelse(Altman <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Altman >= outlier.vals[2], outlier.vals[2], Altman))),
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 7) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator != "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise(mean.nas, n())

@@

H80CS00003
```

@@

```
## Back of the envelop

@@

es.direct <- did2s(
  data = df.z.temp %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
  yname = "Sites", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.indirect <- did2s(
  data = df.z.temp%>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
  yname = "Sites", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

>>>>

@@

## Final DID Event Studies and Alt Estimate Models (Sun-Abraham, TWFE)

es.data <- data.frame(estimator = 0, term = 0, estimate = 0, std.error = 0, Measure = 0)

  model <-  event_study(data = df.temptemptemp,
  yname = "Outcome", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 7)

  es.data <- rbind(es.data, data.frame(model, Measure = colnames(df.temptemp)[(16+k)]))

ess <- es.data[-1,] %>%

  #filter(estimator %notin% c("Callaway and Sant'Anna (2020)","Roth and Sant'Anna (2021)")) %>% 
  filter(estimator == "Gardner (2021)") %>%

  filter(Measure %in% c('Total','Staff','Altman','Pct.MCD','Pct.None','Complexity')) %>% 
  mutate(Group = ifelse(Measure %in% c('Total','Staff','logPatsPerStaff','Qcomp'), "Operational Metrics", 
                        ifelse(Measure %in% c('Altman','LiabPctAssets','months_of_cash'), 'Financial Metrics', 'Selection Metrics'))) %>% 
  rename(Year = term) %>% 
  ggplot(aes(x = Year, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + 
  facet_wrap(Group~Measure, scales = "free_y", ncol = 2)

ess + theme(legend.position="none")
ess + theme(legend.position="bottom")

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value) & value_min > 1) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise(mean.nas(Closed), n())

@@

#H80CS00003
```

@@

## Comparing Rivals with Incumbents
```{r}
  df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
      rbind(df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.x" = "BHCMISID", "Year")) %>% mutate(Type = "Rival")) %>% 
        mutate(Quality = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100) %>% 
      mutate(quick_ratio = as.numeric(quick_ratio),
             Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities) %>% 
      mutate(Liquidity = ifelse(is.infinite(Liquidity), NA, Liquidity), 
         Profitability = ifelse(is.infinite(Profitability), NA, Profitability), 
         Efficiency = ifelse(is.infinite(Efficiency), NA, Efficiency), 
         NetWorth = ifelse(is.infinite(NetWorth), NA, NetWorth), 
         #Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
         Altman = (0.0656 * Liquidity + 0.0326 * quick_ratio + 0.0672 * Efficiency + 0.0105 * NetWorth) * 10) %>% 
      select(Type, Quality, Total, Altman, Pct.NHA:Pct.COM) %>% 
          tbl_summary(by = Type, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"), missing = "no") %>% 
  add_p()

  df.z.dist %>% left_join(df.comp, by = c("BHCMIS ID.y" = "BHCMISID", "Year")) %>% 
      mutate(Type = "Incumbent") %>% 
    group_by(`BHCMIS ID.y`)

  length(unique(df.z.temp2$`BHCMIS ID`))

## Stratified Figure

```{r}
coeffs.strat <- coeffs
coeffs.strat[2,] <- coeffs.strat[2,] / 100

strat.zip.temp <- data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs.strat[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  filter(V1 != "ZipHHI") %>% 
   mutate(LB = Estimate - as.numeric(Std..Error) * 1.96, 
         UB = Estimate + as.numeric(Std..Error) * 1.96) %>% 
  select(V1, Estimate, LB, UB) %>% 
    mutate(Class = "Directly Competitive")%>% 
  rbind(data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs.strat[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  filter(V1 != "ZipHHI") %>% 
   mutate(LB = Estimate.1 - as.numeric(Std..Error.1) * 1.96, 
          UB = Estimate.1 + as.numeric(Std..Error.1) * 1.96) %>% 
    select(V1, Estimate.1, LB, UB) %>% 
    rename(Estimate = Estimate.1) %>% 
    mutate(Class = "Indirectly Competitive")) %>% 
  rename(Outcome = V1) %>% 
  filter(Outcome != "Total.Hours") %>% 
  mutate(Measure = ifelse(Outcome %in% c("Sites","Mean.Hours"), "Access to Care", "Patients and Payer Mix"))

strat.zip.temp$Outcome <- as.factor(strat.zip.temp$Outcome)

p <- strat.zip.temp  %>% 
  filter(Outcome %notin% c("Intensity","CostPerPat")) %>%

## Back of the envelop

@@

es.direct <- did2s(
  data = df.z.temp %>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 1), 
  yname = "Pct.None", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.indirect <- did2s(
  data = df.z.temp%>% filter(Year >= 2012)   %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) %>% filter(Att == 0 | DirectlyTreated == 0), 
  yname = "Pct.None", 
  treatment = "Tx",
  first_stage = ~ 0 | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-7, Inf)) ,
    cluster_var = "ID", 
  verbose = FALSE)

es.zips.none <- cbind(YearRel = c(gsub("rel_year::", "", rownames(es.direct$coeftable)), gsub("rel_year::", "", rownames(es.indirect$coeftable))), 
      rbind(cbind(Group = "Directly",es.direct$coeftable), cbind(Group = "Indirectly",es.indirect$coeftable))) %>% 
  data.frame() %>% 
  mutate(estimate = as.numeric(Estimate), 
         std.error = as.numeric(Std..Error), 
         YearRel = as.numeric(YearRel)) %>% 
  filter(abs(YearRel) <= 6) %>% 
 ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") + ggtitle("Uninsured, %")

ggarrange(es.zips.hours, es.zips.sites, es.zips.mcd, es.zips.none, nrow = 2, ncol = 2, common.legend = TRUE)
